OOPSLA Round 2 Cover Letter \\ {\large Paper \#177: Stateless Model Checking with Data-Race Preemption Points}

### 2016-07-20 oopsla-16/coverletter/letter.tex
tweak letter

\usepackage[charter]{mathdesign}
%\usepackage{fullpage}

\title{OOPSLA Round 2 Cover Letter \\ {\normalsize Paper \#177: Stateless Model Checking with Data-Race Preemption Points}}
\author{Ben Blum (\textsf{bblum@cs.cmu.edu}) \and Garth Gibson (\textsf{garth@cs.cmu.edu})}
\date{July 19, 2016}

@@

\begin{itemize}
	\item Updated several of the experiments in our evaluation.
		\begin{itemize}
			\item Most importantly, we discovered a bug in our implementation of SSS-MC-Shared-Mem which caused it to ignore many shared memory PPs, leading it to find far too few bugs and erroneously declare too many verifications.
		We fixed the bug and re-ran this experiment, leading to the updated data series shown in Figures 7 and 8 and Table 1;
		the new results show increased bug-finding capacity (still not as good as Quicksand) and much slower verification speed.
		We removed the discussion of SSS-MC-Shared-Mem's potential unsoundness from section 6.3 (no longer necessary to justify its position on Figure 8),
		and updated the overall bug-finding ratio between QS-Limited-HB and SSS-MC from 1.5x to 1.25x (pages 1 and 10).
			\item We fixed several other minor bugs in our test cases, leading to slightly changed statistics in Table 1 but no significant difference to the layout of our performance graphs.
		\end{itemize}
	\item Clarified in section 2.2 that Figure 3 is a contrived example (page 3).
	\item Clarified in section 2.2 the advantage offered by Limited HB and the possibility of false negatives (page 3).
	\item Mentioned in section 5.2 the possibility, and downside, of avoiding malloc-recycle false positives by using a hacked allocator (page 8).
	\item Added analysis of ICB preemption bound distribution in section 6.3 (page 11) and Table 2 (page 12) to defuse concerns about possible bias in our suite of bugs.
	\item Mentioned the possibility for future work to occasionally prioritize bigger jobs over small ones in section 7 (page 13).
	\item Reduced clutter among citations, removing ISBNs, DOIs, ``In Proceedings of the Xth annual...'', and so on.
\end{itemize}

@@

\noindent Ben Blum \\
Garth Gibson

>>>>

\usepackage[charter]{mathdesign}
\usepackage{fullpage}

\title{OOPSLA Round 2 Cover Letter \\ {\large Paper \#177: Stateless Model Checking with Data-Race Preemption Points}}
\author{Ben Blum (\textsf{bblum@cs.cmu.edu}) \and Garth Gibson (\textsf{garth@cs.cmu.edu})}
\date{July 19, 2016}

@@

\begin{itemize}
	\item Updated several of the experiments in our evaluation.
		\begin{itemize}
			\item Most importantly, we discovered a bug in our implementation of SSS-MC-Shared-Mem which caused it to ignore many shared memory PPs, leading it to find far too few bugs and erroneously declare too many verifications.
		We fixed the bug and re-ran this experiment, leading to the updated data series shown in Figures 7 and 8 and Table 1;
		the new results show increased bug-finding capacity (still not as good as Quicksand) and much slower verification speed.
		We removed the discussion of SSS-MC-Shared-Mem's potential unsoundness from section 6.3 (no longer necessary to justify its position on Figure 8),
		and updated the overall bug-finding ratio between QS-Limited-HB and SSS-MC from 1.5x to 1.25x (pages 1 and 10).
			\item We fixed several other minor bugs in our test cases, leading to slightly changed statistics in Table 1 but no significant difference to the layout of our performance graphs.
		\end{itemize}
	\item Clarified in section 2.2 that Figure 3 is a contrived example (page 3).
	\item Clarified in section 2.2 the advantage offered by Limited HB and the possibility of false negatives (page 3).
	\item Mentioned in section 5.2 the possibility, and downside, of avoiding malloc-recycle false positives by using a hacked allocator (page 8).
	\item Added analysis of ICB preemption bound distribution in section 6.3 (page 11) and Table 2 (page 12) to defuse concerns about possible bias in our suite of bugs.
	\item Mentioned the possibility for future work to occasionally prioritize bigger jobs over small ones in section 7 (page 13).
	\item Reduced clutter among citations, removing ISBNs, DOIs, ``In Proceedings of the Xth Annual...'', and so on.
\end{itemize}

@@

\noindent Ben Blum \\
Garth Gibson
\thispagestyle{empty}
